### 2019-08-15 thesis.tex
*** empty log message ***

\section{How all of this is related to this work?}
\label{sec:corona}
The source of the tenuous magnetized plasma permeating the heliosphere,
and also the origin of the dangerous solar output disturbing the near-Earth
environment, is the outermost layer of the Sun: the solar corona. The solar
corona can be easily recognized as the bright halo that appears around the
hidden Sun during solar eclipses. \autoref{corona} shows a beautiful
photograph of the corona, taken in the $2017$’s solar eclipse. In the picture,
one can see the moon covering the bright chromosphere, allowing us to have
a glimpse of the thin, but ultra-hot coronal plasma.

\begin{figure}[hb]
  \begin{center}
    \includegraphics[width=0.892\textwidth]{corona2017.png}
    %\includegraphics[width=0.4305\textwidth]{high-contrast-corona.png}
    \caption{Solar corona captured during the total solar eclipse of 2017.
      {\footnotesize Credit:}
      \href{https://hdr-astrophotography.com/high-resolution-2017-total-solar-eclipse/}
      {\footnotesize Nicolas Lefaudeux}{\footnotesize , accessed at 05/06/2019}.}
    \label{corona}
  \end{center}
\end{figure}

>>>>

\subsection{The solar corona}
\label{sec:corona}
The source of the tenuous magnetized plasma permeating the heliosphere, and
also the origin of solar particles and radiation that may cause disruptive
space weather around Earth, is the outermost layer of the Sun: the solar
corona \cite{Cranmer2017,Klein2017}. The solar corona can be easily recognized
as the bright halo that appears around the hidden Sun during solar eclipses.
\autoref{corona} shows two beautiful photographs of the corona, taken in two
different solar eclipses, August 21 $2017$ and $2019$. In both pictures, one
can see the moon covering the bright photosphere, allowing us to have a
glimpse of the thin, but ultra-hot coronal plasma. Non-intuitively, the solar
corona is, at the same time, the thinnest and the hottest outer layer of
the Sun, where the temperature is of the order of $10^6\unit{K}$.

\begin{figure}[hb]
  \begin{center}
    \includegraphics[width=0.892\textwidth]{corona2017.png}
    \includegraphics[width=0.892\textwidth]{corona2019.png}
    \caption{Solar corona captured during the total solar eclipse of 2017 (top panel)
      and 2019 (lower panel). The reddish contour at some regions is the chromosphere,
      and the reddish arcs are solar prominences, chromospheric plasma structures that
      penetrate the coronal region \cite{BenzA2002,Habbal2010,JeanVlaude2015}.
      {\footnotesize Credit:}
      \href{https://hdr-astrophotography.com}
      {\footnotesize Nicolas Lefaudeux}{\footnotesize , accessed at 15/08/2019}.}
    \label{corona}
  \end{center}
\end{figure}
